A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-16 paper/paper.tex
Shrunk example tables and moved subcaptions to top
Simplified example graph commands

\newcommand{\examplexG}[5] {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=5] {
                    1[label=90:#1],2[label=0:#2],3[label=0:#3],4[label=180:#4],5[label=180:#5];
            1--4; 1--5; 2--3; 2--5; 3--5;
        };
    }
    \end{minipage}
}
\newcommand{\examplexH}[6] {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=6, phase=60] {
                    a[label=0:#1],b[label=0:#2],c[label=0:#3],d[label=180:#4],e[label=180:#5],f[label=180:#6];
            a--b; a--c; a--e; b--d; b--f; c--d; c--e; c--f; d--f; e--f;
        };
    }
    \end{minipage}
}

\newcommand{\LabelTables}[4] {
  \centering
  \begin{minipage}[t]{#1\linewidth}
      Mapping

      \bigskip

      #2
  \end{minipage}
  \quad
  \begin{minipage}[t]{0.3\linewidth}
      \centering
      Labelling of $G$
      \begin{tabular}[t]{cc}
      \toprule
          Vertex & Label\\
      \midrule
          #3
      \bottomrule
      \end{tabular}
  \end{minipage}
  \quad
  \begin{minipage}[t]{0.3\linewidth}
      \centering
      Labelling of $H$
      \begin{tabular}[t]{cc}
      \toprule
          Vertex & Label\\
      \midrule
          #4
      \bottomrule
      \end{tabular}
      \medskip
  \end{minipage}
}

@@

\begin{figure}[t]
\centering
    \examplexG{}{}{}{}{}
    \examplexH{}{}{}{}{}{}
\caption{Example graphs $G$ and $H$.}
\label{fig:alg1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \subfigure[][After mapping $1$ to $a$] {
      \LabelTables{.15}
                  {$\{1a\}$}
                  {$2$ & 0 \\
                   $3$ & 0 \\
                   $4$ & 1 \\
                   $5$ & 1 \\}
                  {$b$ & 1 \\
                   $c$ & 1 \\
                   $d$ & 0 \\
                   $e$ & 1 \\
                   $f$ & 0 \\}
      \label{fig:alg2}
    }

    \subfigure[][After mapping $2$ to $d$] {
      \LabelTables{.15}
                  {$\{1a,2d\}$}
                  {$3$ & 01 \\
                   $4$ & 10 \\
                   $5$ & 11 \\}
                  {$b$ & 11 \\
                   $c$ & 11 \\
                   $e$ & 10 \\
                   $f$ & 01 \\}
      \label{fig:alg3}
    }

    \subfigure[][After mapping $3$ to $f$] {
      \LabelTables{.2}
                  {$\{1a,2d,3f\}$}
                  {$4$ & 100 \\
                   $5$ & 111 \\}
                  {$b$ & 111 \\
                   $c$ & 111 \\
                   $e$ & 101 \\}
      \label{fig:alg4}
    }

@@

\begin{figure}[t]
    \centering
    \subfigure[][Unlabelled, undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-cumulative.pdf}
        \label{figure:plain-cumulative}
    }

@@

\begin{figure}[t]
    \centering
    \subfigure[][Unlabelled, undirected, connected instances] {
        \centering
        \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
        \label{figure:plain-connected-cumulative}
    }

>>>>

\newcommand{\exampleG} {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=5] {
                    1,2,3,4,5;
            1--4; 1--5; 2--3; 2--5; 3--5;
        };
    }
    \end{minipage}
}
\newcommand{\exampleH} {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=6, phase=60] {
                    a,b,c,d,e,f;
            a--b; a--c; a--e; b--d; b--f; c--d; c--e; c--f; d--f; e--f;
        };
    }
    \end{minipage}
}

\newcommand{\LabelTables}[3] {
  {\footnotesize
    \centering
    \begin{minipage}[t]{.17\linewidth}
        Mapping

        \bigskip\vspace{-4pt}

        #1
    \end{minipage}
    \quad
    \begin{minipage}[t]{0.31\linewidth}
        \centering
        Labelling of $G$\vspace{-4pt}
        \begin{tabular}[t]{cc}
        \toprule
            Vertex & Label\\
        \midrule
            #2
        \bottomrule
        \end{tabular}
    \end{minipage}
    \quad
    \begin{minipage}[t]{0.31\linewidth}
        \centering
        Labelling of $H$\vspace{-4pt}
        \begin{tabular}[t]{cc}
        \toprule
            Vertex & Label\\
        \midrule
            #3
        \bottomrule
        \end{tabular}
        \medskip
    \end{minipage}
  }
}

@@

\begin{figure}[t]
\centering
    \exampleG
    \exampleH
\caption{Example graphs $G$ and $H$.}
\label{fig:alg1}
\end{figure}

@@

\begin{figure}[h]
    \centering\subfiguretopcaptrue
    \subfigure[][After mapping $1$ to $a$] {
      \LabelTables{$\{1a\}$}
                  {$2$ & 0 \\
                   $3$ & 0 \\
                   $4$ & 1 \\
                   $5$ & 1 \\}
                  {$b$ & 1 \\
                   $c$ & 1 \\
                   $d$ & 0 \\
                   $e$ & 1 \\
                   $f$ & 0 \\}
      \label{fig:alg2}
    }

    \subfigure[][After mapping $2$ to $d$] {
      \LabelTables{$\{1a,2d\}$}
                  {$3$ & 01 \\
                   $4$ & 10 \\
                   $5$ & 11 \\}
                  {$b$ & 11 \\
                   $c$ & 11 \\
                   $e$ & 10 \\
                   $f$ & 01 \\}
      \label{fig:alg3}
    }

    \subfigure[][After mapping $3$ to $f$] {
      \LabelTables{$\{1a,2d,3f\}$}
                  {$4$ & 100 \\
                   $5$ & 111 \\}
                  {$b$ & 111 \\
                   $c$ & 111 \\
                   $e$ & 101 \\}
      \label{fig:alg4}
    }

@@

\begin{figure}[t]
    \centering\subfiguretopcaptrue
    \subfigure[][Unlabelled, undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-cumulative.pdf}
        \label{figure:plain-cumulative}
    }

@@

\begin{figure}[t]
    \centering\subfiguretopcaptrue
    \subfigure[][Unlabelled, undirected, connected instances] {
        \centering
        \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
        \label{figure:plain-connected-cumulative}
    }
